Working title: the most amaz-zing SPIM and how we built it.

### 2015-01-13 latex-style-files-spie-manuscript/manuscript1.0.tex
- new y axis scale on mouse brain size graph to include ludos new calculations - marcel's text crudely inserted and needs extensive review

		Fluorescence is collected on a axis perpendicular to the excitation with an objective that was specifically designed for immersion in clearing solutions of various refractive indices. The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP). To image the whole volume of interest the objective has a relatively low magnification of 25x and a large working distance of 8mm yet a high numerical aperture (1.0NA) affords high resolution imaging. HERE WE'LL NEED SOME CHARACTERISATION DATA. We use a tube lens of 200mm to create an image on a sCMOS camera (Orca Flash4.0, Hamamatsu). A fluorescent filter is used to block out any excitation light. The camera chip of over 4 megapixels is read out in one sweep from top to bottom in the so-called light sheet mode in which only a subset of horizontal lines is exposed and consequently read out and any time. This sweeping line exposure creates a virtual confocal slit. Confocality is achieved by synchronising a single line which generates the light sheet with the exposure of a few lines on the CMOS chip.

@@

The microscope was designed and developed by optical technology specialists yet needs to be operational in a multi-user environment. The greatest challenge consists in making the use of the microscope easy and intuitive such that no formidable expertise is needed when it is operated by interdisciplinary researchers. Another aspect of software design is avoiding redundancy in writing software, for example, when a second or third microscope with basic similarity yet slightly specialised equipment is being designed in the same laboratory. Writing well structured scientific software in a group of researchers is an often recurring challenge. The final code should be the common effort of all contributors each with their own know-how and practical expertise. We chose to write our software in LabVIEW (National Instruments), as this language is particularly well suited to hardware control and data acquisition by pre-developed methods.

The Murmex library, developed by one of the co-authors, helps users to collaborate on software development by letting them independently create their contribution to the software within a  standardized programming scheme by employing object oriented programming methodology. Murmex uses the library LabbitMQ, which is a wrapper of RabbitMQ, a message-oriented middleware facilitating message shipment and receival. These layers of abstraction are mostly hidden for the developers.

RabbitMQ
The RabbitMQ server (message broker) needs to be installed either locally or somewhere in the network. The message-based communication allows for buffered, asynchronous and reliable message communication between several software components. Messages are routed by the broker to the specific software component by its ID. In order to access the functionality of RabbitMQ, the application programming interface (API) \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/211065}{LabbitMQ} was used, which uses .NET calls for sending and receiving messages to and from the RabbitMQ broker. Messages can be sent to a single recipient by its ID or sent to all available components.

Murmex
The \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/212895}{Murmex library} is a software development kit for creating distributed finite state machines in LabVIEW (2012 and newer). A finite state machine resembles the Strategy pattern [Design Patterns: Elements of Reusable Object-Oriented Software, E. Gamma, R. Helm, R. Johnson, J. Vlissides, 1994], which lets the software of one component proceed from one particular state to another based on message it receives from itself or other components (for example to execute Initialise, Start, Proceed, Stop, Terminate). In each state it executes the code for that state only, but flexible execution patterns are possible. It thus allows for predictable behaviour, without knowing the exact code. Murmex has twelve pre-defined common states (e.g. Initialise, Start, Stop, Terminate) and a generic state for implementing custom states. A software component that represents one, yet large, task, often uses only those previously four mentioned states. Examples for such a software component are the implementation a laser, translation stage and a camera.

@@

\section{Data}
	\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[height=16cm]{LSMdata.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:LSMdata} Whole mouse brain tomography. Imaging of whole transgenic mouse brains treated with CLARITY and cleared with TDE 63\% imaged with LSM (Olympus, 25X objective). (A) 3D rendering of a parvalbumin-dTomato brain. (B) 3D rendering of stacks from PV-dTomato mouse brain, GAD-dTomato mouse brain,  PI stained mouse brain, FITC-albumin labeled mouse brain, scale bar = 400 µm. (C,D,E,F) High resolution insert, of the stack corresponding to red boxes in C. Scale bar = 100 µm.} 
   \end{figure}

>>>>

		Fluorescence is collected on a axis perpendicular to the excitation with an objective that was specifically designed for immersion in clearing solutions of various refractive indices. The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP). To image the whole volume of interest the objective has a relatively low magnification of 25x and a large working distance of 8mm yet a high numerical aperture (1.0NA) affords high resolution imaging. HERE WE'LL NEED SOME CHARACTERISATION DATA. An overview of imaging properties and derived quantities is given in Table\ref{tab:resolution}. We use a tube lens of 200mm to create an image on a sCMOS camera (Orca Flash4.0, Hamamatsu). A fluorescent filter is used to block out any excitation light. The camera chip of over 4 megapixels is read out in one sweep from top to bottom in the so-called light sheet mode in which only a subset of horizontal lines is exposed and consequently read out and any time. This sweeping line exposure creates a virtual confocal slit. Confocality is achieved by synchronising a single line which generates the light sheet with the exposure of a few lines on the CMOS chip.

@@

The microscope was designed and developed by optical technology specialists yet needs to be operational in a multi-user environment. The greatest challenge consists in making the use of the microscope easy and intuitive such that no formidable expertise is needed when it is operated by interdisciplinary researchers. Another aspect of software design is avoiding redundancy in writing software, for example, when a second or third microscope with basic similarity yet slightly specialised equipment is being designed in the same laboratory. Writing well structured scientific software in a group of researchers is an often recurring challenge. The final code should be the common effort of all contributors each with their own know-how and practical expertise. Contemporary experimental research often relies on the acquisition and real-time processing of various data streams. In a given experiment, data may be acquired from multiple, even spatially separated sources, while individual processing steps may be computationally intensive and need to be distributed over several computers to be performed on-line. We chose to write our software in LabVIEW (National Instruments), as this language is particularly well suited to hardware control and data acquisition by pre-developed methods, using the Murmex library. The Murmex library, developed by one of the co-authors, helps users to collaborate on software development by letting them independently create their respective contributions to the software within a standardized programming scheme by employing object oriented programming methodology (OOP). Murmex uses the library LabbitMQ, which is a wrapper of RabbitMQ, a message-oriented middle ware facilitating message shipment and receival. These layers of abstraction are mostly hidden for the developers.

\subsection{Object oriented programming}
In OOP the developer creates classes, which are data structures that contain private data and methods that perform actions on the data. LabVIEW supports classes since 2006, but got to its mature form with LabVIEW 2009. When you create a subclass (child) from the toplevel class (parent), you automatically inherit its methods and data. Public methods can be called by the child, while private methods are only accessible by the owning class. A method implemented by the parent, which has the Dynamic Dispatch enabled and is public, can be replaced or augmented by the child. The parent can force the child to call its method or allow to ignore its code. A call to such a dynamic and public method is chained, it thus calls first the child method, which perform the action before or after calling the parent. The parent calls again its parent before or after executing its code and thus create a complete call chain for a single method.
Next to the methods, the classes have private class data, which can only be accessed by the owning class. In order to give access to its data, a method needs to have methods accessing the data. The instance created at runtime from a class is called the object. Many objects can be made from a class, like many pies can be made from a pie recipe. Next, each object runs independently and contains its own data.

\subsection{RabbitMQ}
The RabbitMQ server (message broker) needs to be installed either locally or somewhere in the network. The message-based communication allows for buffered, asynchronous and reliable message communication between several software components. Messages are routed by the broker to the specific software component by its ID. In order to access the functionality of RabbitMQ, the application programming interface (API) \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/211065}{LabbitMQ} was used, which uses .NET calls for sending and receiving messages to and from the RabbitMQ broker. Messages can be sent to a single recipient by its ID or sent to all available components.

\subsection{Murmex}
The \href{http://sine.ni.com/nips/cds/view/p/lang/en/nid/212895}{Murmex library} is a software development kit for creating distributed finite state machines in LabVIEW (2012 and newer). A finite state machine resembles the Strategy pattern [Design Patterns: Elements of Reusable Object-Oriented Software, E. Gamma, R. Helm, R. Johnson, J. Vlissides, 1994], which lets the software of one component proceed from one particular state to another based on message it receives from itself or other components (for example to execute Initialise, Start, Proceed, Stop, Terminate). In each state it executes the code for that state only, but flexible execution patterns are possible. It thus allows for predictable behaviour, without knowing the exact code. Murmex has twelve pre-defined common states (e.g. Initialise, Start, Stop, Terminate) and a generic state for implementing custom states. A software component that represents one, yet large, task, often uses only those previously four mentioned states. Examples for such a software component are the implementation of a laser, a translation stage and a camera. Such a component would implement in the Initialise method the initialisation of the communication port to the device, start activity in the Start method, stop activity in the Stop method and close the communication and free up memory in the Terminate. 
While each component is an autonomous program, variables on which each component might depend, have to be shared among the components. The Update method is used for this purpose, which allows components to update itself with new parameters and automatically forward these parameters to down- or upstream components by using a mapping script $(e.g. datastorage.total_movie_size=xres*yres*number_of_frames, where datastorage is the ID of the recipient, total_movie_size is the name of the parameter to be updated and xres, yres and number_of_frames are the names of parameters of the sender)$.
Typically, a Murmex component streams data only to components listed as observers in its configuration file. Using this concept, components can be configured to form arbitrarily complex signal processing pipelines or networks. Once a component has been considered to be stable by the developer, an executable can be built. An important component named ServiceManager (also based on Murmex) can communicate to other ServiceManagers over the network or internet and can start remotely executables. This allows the user to start up a sophisticated configuration with multiple components as executable on different computers, but steered from one computer.

@@

\section{Data}

	\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[height=16cm]{LSMdata.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:LSMdata} Whole mouse brain tomography. Imaging of whole transgenic mouse brains treated with CLARITY and cleared with TDE 63\% imaged with LSM (Olympus, 25X objective). (A) 3D rendering of a parvalbumin-dTomato brain. (B) 3D rendering of stacks from PV-dTomato mouse brain, GAD-dTomato mouse brain,  PI stained mouse brain, FITC-albumin labeled mouse brain, scale bar = 400 µm. (C,D,E,F) High resolution insert, of the stack corresponding to red boxes in C. Scale bar = 100 µm.} 
   \end{figure}

	Everybody take a look at Figure\ref{fig:LSMdata} because it is the best we have.
